---
title: "Backtesting"
output:
  html_document:
    df_print: paged
runtime: shiny
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r load dt balance data, include=FALSE}
rm(list=ls())
library(readr)
library(ggplot2)
library(grid)
library(gridExtra)
library(Hmisc)
library(tidyverse)
library(lubridate)
library(data.table)
library(ecm)
library(urca)
library(vars)
library(plyr) 
library(readr)
library(ggplot2)
library(grid)
library(gridExtra)
library(Hmisc)
library(tidyverse)
library(lubridate)
library(plyr)
library(urca)
library(TTR)
library(xts)

```

Graph
```{r, echo = FALSE}
library(shiny)
sliderInput("threshold", "Amount:", min = 0, max = 4, value = 2,step = 0.1)
y <- readRDS("dt.rds")
lookback =16

renderPlot({


total = y %>% 
  mutate(excute = ifelse(abs(mktVal)>input$threshold,  mktVal, 0),
         et.xbidyask = dt.sell.y - beta_ols*dt.sell.x , #notice buy.y > last.y > sell.y
         et.ybidxask = dt.buy.y - beta_ols*dt.buy.x, #notice sell.x > last.x > buy.x
         et.ahead = lead(et,lookback),
         et.real = ifelse(et<0, et.ybidxask, et.xbidyask), # if et<0, we should buy y sell 1.02x
         et.real_ahead = lead(et.real,lookback), # hold the asset after 17 periods
         et.real.reverse = ifelse(et>0, et.ybidxask, et.xbidyask),
         et.real_ahead_reverse = lead(et.real.reverse,lookback),
         profit_close = excute*(et.ahead - et),
         profit_close_fee = excute*(et.ahead - et)  - abs(excute)*dt.last.x * 0.0025,
         profit_bidask = excute*(et.real - et.real_ahead),
         profit_bidask_fee = excute*(et.real - et.real_ahead)  - abs(excute)*dt.last.x * 0.0025,
         cum_profit_close = cumsum(ifelse(is.na(profit_close), 0, profit_close)),
         cum_profit_fee = cumsum(ifelse(is.na(profit_close_fee), 0, profit_close_fee)),
         cum_profit_bidask_fee = cumsum(ifelse(is.na(profit_bidask_fee), 0, profit_bidask_fee)),
         cum_profit_bidask = cumsum(ifelse(is.na(profit_bidask), 0, profit_bidask)),
         time = ymd_hm(dt.utc)
  )

ggplot(data = total) +
  geom_line(aes(x=time,y=cum_profit_bidask))

})
```








Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

